Supplementary Information

### 2020-10-17 doc/manuscript/MEE_manuscript.Rmd
AT comments

For each year in the tree-ring records, we reconstructed $DBH$, as detailed in *Appendix S1*. 
In most cases, when a recent $DBH$ measurement was available, $DBH$ was reconstructed from the outside in. 
In cases where $DBH$ was not available, but when we knew that the core hit pith or could reasonably estimate how far off it was based on the curvature of the rings (DENDORO_REF), $DBH$ was reconstructed from the inside out. 
In either case, we used allometric equations between $DBH$ and bark thickness to account for changes in bark thickness as the tree grew (Appendix S1; Tables S2, S4).

@@

Our analysis consisted of two main steps: (1) identification of the most important climate drivers, and (2) combining $DBH$ and climate drivers into a multivariate model (Fig. `r schematic`). The analysis was run separately for each site and each response variable ($RW$, $BAI$, or $\Delta AGB$).

>>>>

For each year in the tree-ring records, we reconstructed $DBH$, as detailed in *Appendix S1*. 
In most cases, when a recent $DBH$ measurement was available, $DBH$ was reconstructed from the outside in. 
In cases where $DBH$ was not available, but when we knew that the core hit pith or could reasonably estimate how far off it was based on the curvature of the rings [@applequist_simple_1958; @duncan_evaluation_1989], $DBH$ was reconstructed from the inside out. 
In either case, we used allometric equations between $DBH$ and bark thickness to account for changes in bark thickness as the tree grew (Appendix S1; Tables S2, S4).

@@

Our analysis consisted of two main steps: (1) identification of the most important climate drivers and the time window over which they operate, and (2) combining $DBH$ and climate drivers into a multivariate model (Fig. `r schematic`). The analysis was run separately for each site and each response variable ($RW$, $BAI$, or $\Delta AGB$).
